A Type System for String Sanitation\\Implemented Inside a Python

### 2014-08-01 sanitation-psp14/sanitation-psp14.tex
deprecated old confusing proof.

\begin{thm}
  Let $P$ be a term in the target language. If $\tctx \vdash P : \theta$ 
  then $P \sreduces P'$ and $P' : \theta$.
\end{thm}
\begin{proof}
The proof proceeds by induction on the typing relation and is trivial give
and inversion lemma for the typing relation. \texbf{We can write up this proof if we end up having enough space...}
\end{proof}

@@

\begin{thm}
If $S : \strin{r}$ then there exists a T such that $\trden{s} = T$ and either: 
\begin{description}
  \item[(a)] $T \treduces \tstr{s}$ and $S \sreduces \strin{s}$, and $s \in lang{r}$.
  \item[(b)] $T \err$ and $S \err$.
  \end{description}
\end{thm}
\begin{proof}
By induction on the derivation of $\trden{S} = T$. TODO-nrf add case magic.
\begin{description}
\item[Tr-string] By assumption $\trden{S} = \tstr{s}$. The (a) property follows.
By S-E-Str, $S \sreduces \str{s}$ and by T-E-Str, $\tstr{s} \treduces \tstr{s}$.
By source language type safety, it follows that $s \in \lang{r}$.
\item[Tr-Concat]
By inversion of the typing relaiton for the source lnaguage, $S_1 : \strin{r_1}$ and $S_2 : \stringin{S_2}$.
By induction on the left premise, $T_1 \treduces \tstr{s_1}$, $S_1 \sreduces \str{s_1}$ and $s_1 \in \lang{r_1}$
or else $T_1 err$. 
Similarly for $T_2$ and $S_2$.
In the error cases, the propagations rules corresponding to S-E-Concat and T-E-Concat imply that $\tconcat{T_1}{T_2} \err$ and $\rsconcat{S_1}{S_2} \err$.
In the non-error case, $\rsconcat{S_1}{S_2} \sreduces \strin{s_1 s_2}$ by S-E-Concat and $\tconcat{T_1}{T_2} \treduces \tstr{s_1 s_2}$ by T-E-Concat.
Finally, $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ implies that $s_1 s_2 \in \lang{r}$ by \ref{lemmaregex}.
\item[Tr-subst]
Suppose $\sisubst{r}{S_1}{S_2} : \strin{s}$ for some $x$. 
By inverison, $S_1 : \strin{r_1}$ and $S_2 : \strin{r_2}$.
Note that $s : \subst{r}{S_1}{S_2} : \stringin{\tsubst{r}{r_1}{r_2}}$ by S-T-Subst.
By induction, $\trden{S_1} = T_1$ and $\trden{S_2} = T_2$.
Either (a) or (b) holds for each.

>>>>

\begin{thm}
  Let $P$ be a term in the target language. If $\tctx \vdash P : \theta$ 
  then $P \sreduces P'$ and $P' : \theta$.
\end{thm}
\begin{proof}
The proof proceeds by induction on the typing relation and is trivial give
and inversion lemma for the typing relation. \textbf{We can write up this proof if we end up having enough space...}
\end{proof}

@@

\begin{thm}
If $S : \strin{r}$ then there exists a T such that $\trden{s} = T$ and either: 
\begin{description}
  \item[(a)] $T \treduces \tstr{s}$ and $S \sreduces \strin{s}$, and $s \in lang{r}$.
  \item[(b)] $T \err$ and $S \err$.
  \end{description}
\end{thm}
\begin{proof}
  \textbf{This is a proof for a different theorem that was swapped out at some point, 
    and is no longer valid. Working on the new proof now, by induction on the typing
  relation and correct choice of T}.
  By induction on the derivation of $\trden{S} = T$. (is this an old proof?) 
\begin{description}
\item[Tr-string] By assumption $\trden{S} = \tstr{s}$. The (a) property follows.
By S-E-Str, $S \sreduces \str{s}$ and by T-E-Str, $\tstr{s} \treduces \tstr{s}$.
By source language type safety, it follows that $s \in \lang{r}$.
\item[Tr-Concat]
By inversion of the typing relaiton for the source lnaguage, $S_1 : \strin{r_1}$ and $S_2 : \stringin{S_2}$.
By induction on the left premise, $T_1 \treduces \tstr{s_1}$, $S_1 \sreduces \str{s_1}$ and $s_1 \in \lang{r_1}$
or else $T_1 err$. 
Similarly for $T_2$ and $S_2$.
In the error cases, the propagations rules corresponding to S-E-Concat and T-E-Concat imply that $\tconcat{T_1}{T_2} \err$ and $\rsconcat{S_1}{S_2} \err$.
In the non-error case, $\rsconcat{S_1}{S_2} \sreduces \strin{s_1 s_2}$ by S-E-Concat and $\tconcat{T_1}{T_2} \treduces \tstr{s_1 s_2}$ by T-E-Concat.
Finally, $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ implies that $s_1 s_2 \in \lang{r}$ by \ref{lemmaregex}.
\item[Tr-subst]
Suppose $\sisubst{r}{S_1}{S_2} : \strin{s}$ for some $x$. 
By inverison, $S_1 : \strin{r_1}$ and $S_2 : \strin{r_2}$.
Note that $s : \subst{r}{S_1}{S_2} : \stringin{\tsubst{r}{r_1}{r_2}}$ by S-T-Subst.
By induction, $\trden{S_1} = T_1$ and $\trden{S_2} = T_2$.
Either (a) or (b) holds for each.
